### 2025-07-03 Text/Thesis/Chapters/Chapter2.qmd
update derivations in main text

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation}
provided $\alpha <-r$, and infinite otherwise.
Therefore, assuming $\alpha<-1$, its expected value is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
\end{equation}

@@

This section details the closed-form expressions for $H$, $R_\lambda$, and $T_\lambda$ under $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ models. Shannon entropy derivations are taken from literature and adapted to our parametrisation, whereas the Rényi and Tsallis expressions are original contributions derived as part of this research (see Appendix&nbsp;\ref{sec-appendix-A}). At the end of the chapter, we summarize the common structure shared by all three measures and illustrate their convergence behavior.

@@

\textbf{Textured case.} In the case of the $\mathcal{G}^0_I$ distribution \eqref{E:gi02}, we adapt existing expressions reported by De A. Ferreira and Nascimento&nbsp;[-@Ferreira2020] to our parametrization, using the relation $\mu = -\gamma/(\alpha + 1)$. This yields:
\begin{multline}
\label{eq:GIO-Sh1}
H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) =H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)\;+\;
\Bigl[ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)
+\ln (-1-\alpha) \\
-\ln\Gamma(L-\alpha) 
+\ln\Gamma(-\alpha)-L\Bigr].
\end{multline}
Equation \eqref{eq:GIO-Sh1} can be interpreted as:  
$$
H(\mathcal{G}^0_I)
=
\underbrace{H\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
\hspace{1.8em} + \hspace{-1.0em}
\underbrace{\Delta_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
$$
\begin{multline} 
\text{where}\quad
  \Delta_\alpha
  =
    (L-\alpha)\,\psi^{(0)}(L-\alpha)
   -(1-\alpha)\,\psi^{(0)}(-\alpha)
   +\ln(-1-\alpha)
\\[-2pt]\hphantom{\Delta^{\mathrm{Sh}}_\alpha={}}
   -\ln\Gamma(L-\alpha)+\ln\Gamma(-\alpha)-L.
   \label{eq:GIO-Sh2}
\end{multline}
the extra term $\Delta_\alpha$ captures how much entropy increases due to texture (heterogeneity), caused by the roughness parameter $\alpha$. When $\alpha \to -\infty$ (fully developed speckle), the excess term tends to zero, and Equation \eqref{eq:GIO-Sh1} collapses to the homogeneous case in \eqref{eq:gamma-sh1}, i.e.,    
$$
\lim_{\alpha \to -\infty} H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
$$ 
Appendix&nbsp;\ref{app:A1} provides a proof of this limiting behavior.
<!-- This motivates our work: we check whether the \emph{excess} is statistically different from zero.  -->
In practice, detecting heterogeneity is equivalent to testing whether $\Delta_\alpha$ is significantly different from zero.

### Rényi Entropy
For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{E:entropy-R}
R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{equation}
As $\lambda \to 1$, $R_\lambda(Z)$ reduces to $H(Z)$.

Using&nbsp;\eqref{E:entropy-R}, we derive closed-form expressions for the Rényi entropy of the $\Gamma_{\mathrm{SAR}}$ and the $\mathcal{G}^0_I$ distributions.

\textbf{Homogeneous case.} We find
\begin{multline}
\label{eq-GammaSAR-R}
R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)
= 
\ln \mu - \ln L + \frac{1}{1-\lambda}
\Bigl[
  -\lambda\,\ln\Gamma(L) + \ln\Gamma\bigl(\lambda(L-1)+1\bigr) -  \bigl(\lambda(L-1)+1\bigr)\,\ln\lambda
\Bigr].
\end{multline}

\textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
\begin{multline}  
\label{eq-HGI0-R}  
R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr) \;+ \;\ln(-1 - \alpha)  
+ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr) \\ 
+ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) - \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
+ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr].  
\end{multline}
 The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.

Equation&nbsp;\eqref{eq-HGI0-R} can be read as:
$$
R_\lambda(\mathcal{G}^0_I)
=
\underbrace{R_\lambda \bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
\hspace{1.8em} + \hspace{-1.0em}
\underbrace{\Delta^R_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
$$
\begin{multline} 
\text{where}\quad
  \Delta^R_\alpha
  =
    \ln(-1 - \alpha)  
+ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr)  
+ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) \\
- \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
+ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr],
   \label{eq:GIO-R2}
\end{multline}
the excess term $\Delta^R_\alpha$ depends on the heterogeneity parameter $\alpha$, and  $\Delta^{\mathrm{R}}_\alpha\to0$ when
$\alpha\to-\infty$, validating the decomposition, i.e.,
$$
\lim_{\alpha \to -\infty} R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
$$ 
Appendix&nbsp;\ref{app:A24} provides proof of this limiting behavior.

@@

For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:

\begin{equation}
\label{eq:tsallis}
T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} dz \Bigr]. 
\end{equation}
In the limit $\lambda\to1$,
  $T_\lambda(Z)\to H(Z)$, making Tsallis a
  one-parameter generalisation of Shannon entropy.

@@

\textbf{Homogeneous case.} We find
\begin{multline}
\label{eq:gammasar-Tsallis}
T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
\frac{1}{\lambda-1}\Bigl\{1-
\exp\Bigl[
(1-\lambda)\ln\mu
+(\lambda-1)\ln L
+\ln\Gamma\bigl(\lambda(L-1)+1\bigr) \\
-\lambda\ln\Gamma(L)
-(\lambda(L-1)+1)\ln\lambda
\Bigr]\Bigr\}.
\end{multline}

  \textbf{Textured case.} For the $\mathcal{G}^0_I$ distribution, we obtain:
  \begin{multline}
  \label{eq:GI0-Tsallis}
  T_\lambda\bigl(\mathcal{G}^0_I(\mu,\alpha,L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)\;+\;\frac{1}{\lambda-1}\,
  \exp\Bigl[
  (1-\lambda)\ln\mu
  +(\lambda-1)\ln L
  +\ln\Gamma\bigl(\lambda(L-1)+1\bigr)
  \\
  -\lambda\ln\Gamma(L)
  \Bigr] 
  {}\times\Bigl\{1-
  \exp\Bigl[
  (1-\lambda)\ln(-\alpha-1)
  +\lambda\ln\Gamma(L-\alpha)
  -\lambda\ln\Gamma(-\alpha) \\
  +\ln\Gamma\bigl(\lambda(1-\alpha)-1\bigr)
  -\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
  \Bigr]\Bigr\}.
  \end{multline}

  The derivation of these results are proven in the Appendix&nbsp;\ref{app:A2}.

  Equation&nbsp;\eqref{eq:GI0-Tsallis} can be interpreted as:
  $$
  T_\lambda(\mathcal{G}^0_I)
  =
  \underbrace{T_\lambda \bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
  \hspace{1.8em} + \hspace{-1.0em}
  \underbrace{\Delta^T_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
  $$
\begin{multline} 
\text{where}\quad
  \Delta^T_\alpha
  =
\frac{1}{\lambda-1}\,
\exp\Bigl[
(1-\lambda)\ln\mu
+(\lambda-1)\ln L
+\ln\Gamma\bigl(\lambda(L-1)+1\bigr)
-\lambda\ln\Gamma(L)
\Bigr] \\
{}\times\Bigl\{1-
\exp\Bigl[
(1-\lambda)\ln(-\alpha-1)
+\lambda\ln\Gamma(L-\alpha)
-\lambda\ln\Gamma(-\alpha) \\
+\ln\Gamma\bigl(\lambda(1-\alpha)-1\bigr)
-\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
\Bigr]\Bigr\},
   \label{eq:GIO-T}
\end{multline}
the excess term $\Delta^T_\alpha$ depends on the heterogeneity parameter $\alpha$, and  $\Delta^T_\alpha\to0$ when
$\alpha\to-\infty$, validating the decomposition, i.e.,
$$
\lim_{\alpha \to -\infty} T_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
$$ 
Appendix&nbsp;\ref{app:A33} provides proof of this limiting behavior.

Figure&nbsp;\ref{fig:entropy-diagram} provides a conceptual overview of the decomposition structure of the differential entropy for the heterogeneous model $\mathcal{G}^0_I$. This entropy is expressed as the sum of a baseline term corresponding to the homogeneous $\Gamma_{\text{SAR}}$ distribution and an excess term $\Delta_\alpha$ that reflects the contribution of texture. The decomposition applies to the three entropy measures considered in this study: Shannon \eqref{eq:GIO-Sh1}, Rényi \eqref{eq-HGI0-R}, and Tsallis \eqref{eq:GI0-Tsallis}. In all cases, the excess term depends on the roughness parameter $\alpha$ and vanishes as $\alpha\to-\infty$, thus recovering the homogeneous case.

```{=latex}
\begin{figure}[H]
    \centering
    \begin{tikzpicture}[
    node distance=1.5cm,
    entropy/.style={rectangle, rounded corners, draw=blue!60, fill=blue!10, thick, minimum width=3cm, align=center, font=\sffamily},
    property/.style={rectangle, draw=orange!60, fill=orange!10, thick, minimum width=3cm, align=center, font=\sffamily},
    arrow/.style={-Stealth, thick}
    ]
    % Tu diagrama aquí...
    \node[entropy] (shannon) {Shannon \ $H(Z)$};
    \node[entropy, right=of shannon] (renyi) {Rényi \ $R_\lambda(Z)$};
    \node[entropy, right=of renyi] (tsallis) {Tsallis \ $T_\lambda(Z)$};

>>>>

The $r$th order moments of the $\mathcal{G}_I^0$ model are
\begin{equation}
E\big(Z^r\big)  = \left(\frac{\gamma}{L}\right)^r\frac{\Gamma(-\alpha-r)}{\Gamma(-\alpha)}\frac{\Gamma(L+r)}{\Gamma(L)}, 
    \label{E:rmom}
\end{equation}
provided $\alpha <-r$, and infinite otherwise.
Therefore, assuming $\alpha<-1$, its expected value is
\begin{equation}
    \mu=\left(\frac{\gamma}{L}\right)\frac{\Gamma(-\alpha-1)}{\Gamma(-\alpha)}\frac{\Gamma(L+1)}{\gamma(L)}=-\frac{\gamma}{\alpha+1}.
    \label{E:mean1}
\end{equation}

@@

This section details the closed-form expressions for $H$, $R_\lambda$, and $T_\lambda$ under $\Gamma_{\text{SAR}}$ and $\mathcal{G}^0_I$ models. Shannon entropy derivations are taken from literature and adapted to our parametrisation, whereas the Rényi and Tsallis expressions are original contributions derived as part of this research. At the end of the chapter, we summarize the common structure shared by all three measures and illustrate their convergence behavior.

@@

\textbf{Textured case.} In the case of the $\mathcal{G}^0_I$ distribution \eqref{E:gi02}, we adapt existing expressions reported by De A. Ferreira and Nascimento&nbsp;[-@Ferreira2020] to our parametrization, using the relation $\mu = -\gamma/(\alpha + 1)$. This yields:
\begin{multline}
\label{eq:GIO-Sh1}
H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) =H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr)\;+\;
\Bigl[ (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)
+\ln (-1-\alpha) \\
-\ln\Gamma(L-\alpha) 
+\ln\Gamma(-\alpha)-L\Bigr].
\end{multline}
Equation \eqref{eq:GIO-Sh1} can be interpreted as: 
\vspace{-15pt}
$$
H(\mathcal{G}^0_I)
=
\underbrace{H\bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
\hspace{1.8em} + \hspace{-1.0em}
\underbrace{\Delta_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
$$
\vspace{-10pt}
where
\vspace{-15pt}
\begin{multline} 
  \Delta_\alpha
  =
    (L-\alpha)\,\psi^{(0)}(L-\alpha)
   -(1-\alpha)\,\psi^{(0)}(-\alpha)
   +\ln(-1-\alpha)
\\[-2pt]\hphantom{\Delta^{\mathrm{Sh}}_\alpha={}}
   -\ln\Gamma(L-\alpha)+\ln\Gamma(-\alpha)-L,
   \label{eq:GIO-Sh2}
\end{multline}
the extra term $\Delta_\alpha$ captures how much entropy increases due to texture (heterogeneity), caused by the roughness parameter $\alpha$. When $\alpha \to -\infty$ (fully developed speckle), the excess term tends to zero, and Equation \eqref{eq:GIO-Sh1} collapses to the homogeneous case in \eqref{eq:gamma-sh1}, i.e.,
\vspace{-15pt}
$$
\lim_{\alpha \to -\infty} H\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = H\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
$$ 
Appendix&nbsp;\ref{app:A1} provides a proof of this limiting behavior.
<!-- This motivates our work: we check whether the \emph{excess} is statistically different from zero.  -->
In practice, detecting heterogeneity is equivalent to testing whether $\Delta_\alpha$ is significantly different from zero.

### Rényi Entropy
For a continuous random variable $Z$ with pdf $f(z)$, the Rényi entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{E:entropy-R}
R_\lambda(Z)  = \frac{1}{1-\lambda }\ln \Bigl[ \mathbb{E}\Bigl( f^{\lambda - 1}(Z)\Bigr) \Bigr] =\frac{1}{1 - \lambda} \ln \int_{-\infty}^{\infty} [f(z)]^\lambda \, dz.
\end{equation}
As $\lambda \to 1$, $R_{\lambda}(Z)$ reduces to the Shannon entropy $H(Z)$.

Using \eqref{E:entropy-R}, we now derive the closed-form expression for the Rényi entropy under the homogeneous ($\Gamma_{\mathrm{SAR}}$) model.

\textbf{Homogeneous case.} Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$ with pdf given in \eqref{E:gamma1}. We compute
$$
I = \int_{0}^{\infty}
    \bigl[f_{\Gamma_{\mathrm{SAR}}}(z;L,\mu)\bigr]^{\lambda}
    \,\mathrm{d}z
  = \Bigl(\tfrac{L^{L}}{\Gamma(L)\,\mu^{L}}\Bigr)^{\!\lambda}
    \int_{0}^{\infty} z^{\lambda(L-1)}
    \exp\Bigl(-\tfrac{\lambda L}{\mu}\,z\Bigr)\,\mathrm{d}z.
$$
Using the Gamma integral identity
\begin{align*}
\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
\end{align*}
with
\vspace{-10pt}
$$
p = \lambda(L-1)+1,\quad
q = \frac{\lambda L}{\mu},
$$
we obtain
$$
I
= \Bigl(\tfrac{L^{L}}{\Gamma(L)\,\mu^{L}}\Bigr)^{\!\lambda}
  \frac{\Gamma\bigl(\lambda(L-1)+1\bigr)}
       {\bigl(\tfrac{\lambda L}{\mu}\bigr)^{\lambda(L-1)+1}}.
$$
Taking logarithms and simplifying gives
\begin{equation*}
\ln I
= (1-\lambda)\bigl(\ln \mu - \ln L\bigr)
- \lambda\,\ln\Gamma(L)
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)
- \bigl(\lambda(L-1)+1\bigr)\ln\lambda.
\end{equation*}
Substituting into \eqref{E:entropy-R} yields the closed-form
\begin{equation}
  \label{eq-GammaSAR-R}
  \boxed{
  R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
  = \ln\mu - \ln L
+ \frac{1}{1-\lambda}
\Bigl[
-\lambda\,\ln\Gamma(L)
+ \ln\Gamma\bigl(\lambda(L-1)+1\bigr)
- \bigl(\lambda(L-1)+1\bigr)\ln\lambda
\Bigr].
}
\end{equation}

\textbf{Textured case.} Starting from the definition of Rényi entropy in  \eqref{E:entropy-R} and the pdf of  $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ given in \eqref{E:gi01}, we define:
$$
I
= \int_{0}^{\infty}\bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
= C^{\lambda}
  \int_{0}^{\infty}
    \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
\qquad
C=\frac{L^L\Gamma(L-\alpha)}{\gamma^{\alpha}\Gamma(-\alpha)\Gamma(L)}.
$$
The parameterisation satisfies $\gamma=-\mu(\alpha+1)$, so the final result will be expressed in terms of $\mu$.

$$
I \;=\;\int_{0}^{\infty}
        \bigl[f_{\mathcal{G}^0_I}(z;\alpha,\gamma,L)\bigr]^{\lambda}\,dz
    \;=\;C^{\lambda}\!
        \int_{0}^{\infty}\!
          \frac{z^{\lambda(L-1)}}{(\gamma+Lz)^{\,\lambda(L-\alpha)}}\,dz,
$$
With the change of variable $t=Lz/\gamma$ ($dz=\gamma\,dt/L$) we obtain:
$$
I
= C^{\lambda}\,
  \frac{\gamma^{\,1+\lambda(\alpha-1)}}{L^{\,1+\lambda(L-1)}}
  \int_{0}^{\infty}
    \frac{t^{\lambda(L-1)}}{(1+t)^{\,\lambda(L-\alpha)}}\,dt.
$$
Using the Beta–function identity
$$
\int_{0}^{\infty}\frac{t^{a-1}}{(1+t)^{a+b}}\,dt
= B(a,b),\;\;
a=\lambda(L-1)+1,\;\;
b=\lambda(-\alpha+1)-1,
$$
it follows that
\vspace{-15pt}
\begin{align*}
I 
&= C^\lambda \,\frac{\gamma^{\,1+\lambda(\alpha - 1)}}{L^{\,1+\lambda(L - 1)}}
   \,B(a,b).
\end{align*}
Next, we note that 
$\gamma^{\,1 + \lambda(\alpha - 1)} = \gamma^{\,1 - \lambda + \lambda\alpha}$ 
and 
$L^{\,1 + \lambda(L - 1)} = L^{\,\lambda L + 1 - \lambda}.$ 
Since
$$
C^\lambda 
= \biggl(\tfrac{L^L}{\gamma^\alpha\,\Gamma(-\alpha)\,\Gamma(L)}\,\Gamma(L - \alpha)\biggr)^{\!\lambda}
= L^{\lambda L}\,\gamma^{-\alpha \lambda}
  \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda,
$$
we obtain
\vspace{-15pt}
\begin{align*}
I
&= \gamma^{\,1 - \lambda}\,
   L^{\,\lambda - 1}
   \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
   \,B(a,b).
\end{align*}
By \eqref{E:entropy-R}, the Rényi entropy, is given by:
\begin{align*}
R_\lambda(Z)
= \frac{1}{\,1 - \lambda\,} \,\ln I=\frac{1}{\,1 - \lambda\,}
  \,\ln\!\Bigl[
    \gamma^{\,1 - \lambda}\,
    L^{\,\lambda - 1}\,
    \Bigl(\tfrac{\Gamma(L - \alpha)}{\Gamma(-\alpha)\,\Gamma(L)}\Bigr)^\lambda
    \,B(a,b)
  \Bigr].
\end{align*}
Thus, for $Z \sim \mathcal{G}^0_I(\alpha, \gamma, L)$,
\begin{align*}
R_\lambda\bigl(\mathcal{G}^0_I(\alpha, \gamma, L)\bigr)
&= \ln\Bigl(\tfrac{\gamma}{\,L}\Bigr)
+ \frac{1}{\,1 - \lambda\,}
    \Bigl[
      \lambda\bigl(\ln \Gamma(L - \alpha)  
- \ln \Gamma(-\alpha) - \ln \Gamma(L)\bigr)
+ \ln B(a,b)
    \Bigr].
\end{align*}
Using the property 
$$
\ln B(a,b) 
= \ln \Gamma(a) + \ln \Gamma(b) - \ln \Gamma(a + b),
$$
where $a + b = \lambda(L - \alpha)$, we have
\begin{multline}
R_\lambda\bigl(\mathcal{G}^0_I( \alpha,\gamma, L)\bigr)
= \ln\Bigl(\tfrac{\gamma}{L}\Bigr)
+ \frac{1}{\,1 - \lambda\,}
\Bigl[
     \lambda\bigl(\ln \Gamma(L - \alpha) 
- \ln \Gamma(-\alpha) 
- \ln \Gamma(L)\bigr)
+ \ln \Gamma(a)
+ \ln \Gamma(b) \\
- \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
\Bigr].
\label{eq:GI0RenyiInGamma1}
\end{multline}
Finally, noting that $\gamma = -\mu(\alpha + 1)$ from \eqref{E:rmom}, and substituting this expression into \eqref{eq:GI0RenyiInGamma1}, we obtain:
\begin{multline*}
R_\lambda\bigl(\mathcal{G}^0_I( \alpha,\mu, L)\bigr)
= \ln \mu  -  \ln L + \ln(- 1-\alpha)
+ \frac{1}{\,1 - \lambda\,}
  \Bigl[
    \lambda\Bigl(\ln \Gamma(L - \alpha) 
- \ln \Gamma(-\alpha) 
- \ln \Gamma(L)\Bigr)\\
+ \ln \Gamma\bigl(\lambda(L - 1) + 1\bigr)
+ \ln \Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr)
- \ln \Gamma\bigl(\lambda(L - \alpha)\bigr)
\Bigr],
\label{eq:RenyiGI0Final}
\end{multline*}
This expression extends the Rényi entropy of the $\Gamma_{\mathrm{SAR}}(L,\mu)$ model \eqref{eq-GammaSAR-R} by including additional terms that depend on the texture parameter $\alpha$. Specifically:
\begin{equation}
\label{eq-HGI0-R}
\boxed{%
\begin{aligned}
R_{\lambda}\bigl(\mathcal{G}^0_I(\alpha,\mu,L)\bigr)
&=R_{\lambda}\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)
  +\ln(-1-\alpha) \\
&\qquad+\,\frac{1}{1-\lambda}\!\bigl[
    \lambda\bigl(\ln\Gamma(L-\alpha)-\ln\Gamma(-\alpha)\bigr)
    +\ln\Gamma\bigl(\lambda(-\alpha+1)-1\bigr) \\
&\hspace{6.9em}-\,\ln\Gamma\bigl(\lambda(L-\alpha)\bigr)
    +\bigl(\lambda(L-1)+1\bigr)\ln\lambda
  \bigr].
\end{aligned}}
\end{equation}
Equation&nbsp;\eqref{eq-HGI0-R} can be read as:
\vspace{-15pt}
\begin{equation*}
R_\lambda(\mathcal{G}^0_I)
=
\underbrace{R_\lambda \bigl(\Gamma_{\mathrm{SAR}}\bigr)}_{\text{baseline entropy}}
\hspace{1.8em} + \hspace{-1.0em}
\underbrace{\Delta^R_\alpha}_{\text{excess entropy caused by texture}}\hspace{-4.0em},
\end{equation*}
\vspace{-10pt}
where
\vspace{-10pt}
\begin{multline} 
  \Delta^R_\alpha
  =
    \ln(-1 - \alpha)  
+ \frac{1}{1 - \lambda} \Bigl[ \lambda\bigl(\ln\Gamma(L - \alpha) - \ln\Gamma(-\alpha)\bigr)  
+ \ln\Gamma\bigl(\lambda(-\alpha + 1) - 1\bigr) \\
- \ln\Gamma\bigl(\lambda(L - \alpha)\bigr) 
+ \bigl(\lambda(L-1)+1\bigr)\ln\lambda \Bigr],
   \label{eq:GIO-R2}
\end{multline}
the excess term $\Delta^R_\alpha$ depends on the heterogeneity parameter $\alpha$, and  $\Delta^{\mathrm{R}}_\alpha\to0$ when
$\alpha\to-\infty$, validating the decomposition, i.e.,
\vspace{-15pt}
$$
\lim_{\alpha \to -\infty} R_\lambda\bigl(\mathcal{G}^0_I(\mu, \alpha, L)\bigr) = R_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L, \mu)\bigr).
$$ 
Appendix&nbsp;\ref{app:A24} provides proof of this limiting behavior.

@@

For a continuous random variable $Z$ with pdf $f(z)$, the Tsallis entropy of order $\lambda \in \mathbbm R_+ \setminus \{1\}$ is defined as:
\begin{equation}
\label{eq:tsallis}
T_\lambda(Z) = \frac{1}{\lambda - 1} \mathbb{E} \Bigl[ 1 - (f(Z))^{\lambda - 1} \Bigr]
= \frac{1}{\lambda - 1} \Bigl[ 1 - \int_{-\infty}^{\infty} \bigl(f(z)\bigr)^{\lambda} dz \Bigr]. 
\end{equation}
In the limit $\lambda\to1$,
  $T_\lambda(Z)\to H(Z)$, making Tsallis a
  one-parameter generalisation of Shannon entropy.

@@

\textbf{Homogeneous case.} 
Let $Z\sim\Gamma_{\mathrm{SAR}}(L,\mu)$  with pdf given by \eqref{E:gamma1}. Define the integral:
\begin{equation*}
J
= \int_0^\infty \left[f_{\Gamma_{\text{SAR}}}(z;L,\mu)\right]^{\lambda} \, dz.
\end{equation*}
Substituting the density function and simplifying constants, we get
\begin{equation*}
J
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \int_0^\infty
     z^{\lambda(L-1)}
     \exp\left(-\frac{\lambda L}{\mu} z\right)\, dz.
\end{equation*}
Using the Gamma integral identity
\begin{align*}
\int_{0}^{\infty} x^{p-1}e^{-q x}\,\mathrm{d}x
&= \frac{\Gamma(p)}{q^{p}}, \quad p,q>0,
\end{align*}
with $p = \lambda(L-1) + 1$ and $q = \frac{\lambda L}{\mu}$. This leads to
\begin{equation*}
J
= \left(\frac{L^L}{\Gamma(L)\,\mu^L}\right)^{\lambda}
  \cdot
  \frac{\Gamma\big(\lambda(L-1)+1\big)}
       {\left(\frac{\lambda L}{\mu}\right)^{\lambda(L-1)+1}}.
\end{equation*}
After rearranging powers of $L$, $\mu$ and $\lambda$, we obtain
\begin{equation}
J
= \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
       \Gamma\big(\lambda(L - 1) + 1\big)}
      {\lambda^{\lambda(L - 1) + 1}\,
       \left[\Gamma(L)\right]^{\lambda}}.
\label{eq:Jgamma1}
\end{equation}
Substituting Equation \eqref{eq:Jgamma1} into the Tsallis entropy definition \eqref{eq:tsallis}, we have:
\begin{equation}
T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big)
= \frac{1}{\lambda - 1}
   \left[
     1 -
     \frac{L^{\lambda - 1}\,\mu^{1 - \lambda}\;
           \Gamma\big(\lambda(L - 1) + 1\big)}
          {\lambda^{\lambda(L - 1) + 1}\;
           \left[\Gamma(L)\right]^{\lambda}}
   \right].
\label{eq:TsallisGammaFinal1}
\end{equation}
This expression can also be written in an equivalent form:
<!-- \begin{equation*} -->
<!-- T_\lambda\big(\Gamma_{\text{SAR}}(L,\mu)\big) -->
<!-- = \frac{1}{\lambda - 1} \left[ -->
<!--    1 - -->
<!--    \mu^{1 - \lambda}\, -->
<!--    L^{\lambda - 1}\, -->
<!--    \lambda^{ - [\lambda(L - 1) + 1] }\, -->
<!--    \Gamma\big(\lambda(L - 1) + 1\big)\, -->
<!--    \Gamma(L)^{ - \lambda} -->
<!-- \right], -->
<!-- \end{equation*} -->
\begin{equation}
\label{eq:gammasar-Tsallis}
\boxed{%
\begin{aligned}
T_\lambda\bigl(\Gamma_{\mathrm{SAR}}(L,\mu)\bigr)=
\frac{1}{\lambda-1}\Bigl\{1-
\exp\Bigl[
(1-\lambda)\ln\mu
+(\lambda-1)\ln L
+\ln\Gamma\bigl(\lambda(L-1)+1\bigr) \\
-\lambda\ln\Gamma(L)
-(\lambda(L-1)+1)\ln\lambda
\Bigr]\Bigr\}.
\end{aligned}}
\end{equation}

\textbf{Textured case.} Starting from the Tsallis definition in \eqref{eq:tsallis} aand the pdf of $Z\sim\mathcal{G}^0_I(\alpha,\gamma,L)$ in \eqref{E:gi01}, define:
\begin{equation*}
J = \int_0^\infty \left[ f_{\mathcal{G}_I^0}(z) \right]^\lambda dz,
\end{equation*}
which, upon substitution of the density, becomes
\begin{equation*}
J = \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
\int_0^\infty \frac{z^{\lambda(L-1)}}{(\gamma + Lz)^{\lambda(L - \alpha)}}  dz.
\label{eq:J_initial}
\end{equation*}
Introducing the change of variables $t = \frac{Lz}{\gamma}$ (so that $z = \frac{\gamma t}{L}$ and $dz = \frac{\gamma}{L} dt$), we obtain
\begin{align}
J &= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
\frac{\gamma}{L} \int_0^\infty \frac{\left( \frac{\gamma t}{L} \right)^{\lambda(L-1)}}
{[\gamma(1 + t)]^{\lambda(L - \alpha)}}  dt\nonumber \\
&= \left[ \frac{L^L \Gamma(L - \alpha)}{\gamma^\alpha \Gamma(-\alpha) \Gamma(L)} \right]^\lambda 
\frac{\gamma^{1 + \lambda(\alpha - 1)}}{L^{1 + \lambda(L-1)}} 
\int_0^\infty t^{\lambda(L-1)} (1 + t)^{-\lambda(L - \alpha)}  dt.
\label{eq:J_transformed1}
\end{align}
This integral matches the Beta function identity
\begin{equation*}
\int_0^\infty \frac{t^{a-1}}{(1+t)^{a+b}} dt = B(a,b) = \frac{\Gamma(a)\Gamma(b)}{\Gamma(a+b)},
\end{equation*}
for parameters
\begin{equation*}
